A data-driven, pixel-level model to improve the precision of \Kepler\ photometry

### 2013-11-13 documents/plm.tex
autoregressive
scalar
small typos

Once we have obtained the $a_{mnm'}$ parameters corresponding to a particular data point $I_{mn}$,
  we can make a \emph{prediction} $I^{\ast}_{mnn}$ for the intensity at that pixel.
By construction of our objective function, this is truly a prediction,
  in the sense that the optimization (or solve) that produced the parameters
  (and thus the prediction)
  did not make use of $I_{mn}$ itself,
  or even any of the pixel values that are nearby in angle or time
  (as described above).
In addition to the predicted pixel value $I^{\ast}_{mnn}$,
  we can also construct a \emph{residual} $\delta_{mn}$ (data minus prediction),
  defined by
\begin{eqnarray}
\delta_{mn} &\equiv& I_{mn} - I^{\ast}_{mnn}
\quad .
\end{eqnarray}

@@

Our new stellar flux estimates,
  what we will call the ``\name\ photometry'',
  is constructed from the \name\ pixels
  in precisely the same way as the official \Kepler\ SAP photometry
  is constructed from the Target Pixel Files.
That is, we perform a weighted sum of \name\ pixels $J_{mn}$ with weights $w_m$,
  all of which are either zero or unity,
  and we adopt precisely the same weight assignments as are adopted in the SAP photometry;
  in equations, the flux estimate $S_n$ at time $t_n$ of the target star is given by
\begin{eqnarray}
S_n = \frac{1}{N_m}\,\sum_n w_m\,J_{mn}
\quad .
\end{eqnarray}
As we have noted above and below, these photometric estimators are not optimal for any purpose,
  but improving them is beyond the scope of this project.

@@

Then we want to show some kind of scatter plot, which is some variance estimate from us,
  vs the same estimate from the PDC,
  to show that we always or usually win.

@@

>>>>

Once we have obtained the parameters $a_{mnm'}$ corresponding to a particular data point $I_{mn}$,
  we can make a \emph{prediction} $I^{\ast}_{mnn}$ for the intensity at that pixel.
By construction of our objective function, this is truly a prediction,
  in the sense that the optimization (or solve) that produced the parameters
  (and thus the prediction)
  did not make use of $I_{mn}$ itself,
  or even any of the pixel values that are nearby in angle or time
  (as described above).
In addition to the predicted pixel value $I^{\ast}_{mnn}$,
  we can also construct a \emph{residual} $\delta_{mn}$ (data minus prediction),
  defined by
\begin{eqnarray}
\delta_{mn} &\equiv& I_{mn} - I^{\ast}_{mnn}
\quad .
\end{eqnarray}

@@

Our new stellar flux estimates,
  what we will call the ``\name\ photometry'',
  is constructed from the \name\ pixels
  in precisely the same way as the official \Kepler\ SAP photometry
  is constructed from the Target Pixel Files.
That is, we perform a weighted sum of \name\ pixels $J_{mn}$ with weights $w_m$,
  all of which are either zero or unity,
  and we adopt precisely the same weight assignments as are adopted in the SAP photometry;
  in equations, the flux estimate $S_n$ at time $t_n$ of the target star is given by
\begin{eqnarray}
S_n = \frac{1}{M}\,\sum_m w_m\,J_{mn}
\quad ,
\end{eqnarray}
where the sum is over the $M$ pixels that are associated with the target star.
As we have noted above and below, these photometric estimators are not optimal for any purpose,
  but improving them is beyond the scope of this project.

@@

Then we want to show some kind of scatter plot, which is some variance estimate from us,
  vs the same estimate from the PDC,
  to show that we always or usually win.
This variance estimate should be something like the power in the residuals at frequencies
  corresponding to 30-hour periods or maybe 50-hour periods or something like that.

@@

The potential for autoregressive models.  Cite the white paper.
